Semi-Permeable Vesicles: Mathematical Formulation, Numerics, and Physics

### 2020-12-07 vesicle_code/docs/permeableVes/main.tex
edits to PNAS
yny

\affil[a]{Department of Scientific Computing, Florida State University}
\affil[b]{Department of Mathematical Sciences, New Jeresey Institute of
Technology}

@@

\dropcap{T}his PNAS journal template is provided to help you write your
work in the correct journal format. Instructions for use are provided
below. We do not start with a section heading for the introduction, but
rather type the intro starting here.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Shear Flow}
\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/shearComposite.tikz}
  \fi
  \caption{\label{fig:shearComposite} (a) The reduced area of a
  semi-permeable vesicle with $\beta = 10^{-3}$ initialized with four
  different reduced areas in a shear flow with two different flow rates.
  (b) The steady state shape of a semi-permeable vesicle with varying
  flow rates and semi-permeability rates. The circled vesicles
  correspond to the simulations in part (a).}
  \todo[inline]{$\nu=0.75$ run needs more temporal resolution.}
\end{figure*}

>>>>

\affil[a]{Department of Scientific Computing, Florida State University}
\affil[b]{Department of Mathematical Sciences, New Jeresy Institute of
Technology}

@@

\dropcap{W}ater balance is an essential process in the adaptation of a living cell to its environment \cite{AlbertsMolecularBiology}.  
For example, erythrocytes demonstrate efficient exchange of water to participate in efficient body water homeostasis \cite{SugieIntaglietta2018_AmJPhysiolHCP}.
The cell membrane is permeable to water and water-soluble molecules \cite{Dick1964_JTB,FettiplaceHaydon1980_PhysRev,DeamerBramhall1986_ChemPhysLipids,Grafmueller2019_ABLS}.
In the presence of osmolarity (a contrast in the concentration of a solute impermeable to the membrane), water flows in or out of the membrane to adjust the interior cellular volume. In the red blood cell membrane, aquaporin-1 (AQP1) channels give rise to a much higher water permeability of $\sim 1.8\times 10^{-2}$ cm/s in erythrocytes \cite{YangMaVerkman2001_JBC} while for an artificial lipid bilayer membrane the water permeability is in the range of $10^{-4}-10^{-3}$ cm/s \cite{ThompsonHuang1966_ANYAS,FettiplaceHaydon1980_PhysRev,Grafmueller2019_ABLS}.

 Most modeling of water transport across the membrane focuses on the water flux due to osmolarity. However, the osmotic flux is inevitably coupled with the mechanical effects for a deformable membrane \cite{yao-mor2017}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Shear Flow}
\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/shearComposite.tikz}
  \fi
  \caption{\label{fig:shearComposite} (a) The reduced area of a
  semi-permeable vesicle with $\beta = 10^{-3}$ initialized with four
  different reduced areas in a shear flow with two different flow rates.
  (b) The steady state shape of a semi-permeable vesicle with varying
  flow rates and semi-permeability rates. The circled vesicles
  correspond to the simulations in part (a).}
\end{figure*}
